### 2016-03-10 manuscript.Rnw
fix minor typo

In recent years, R has become an essential part of the toolbox of many
researchers in evolutionary biology. R greatly facilitates the analysis of large
datasets, and allows researchers to combine methods in novel ways because many
methods for comparative analyses are implemented, and because it is a relatively
easy to use programming language. Additionally, as more data are made available
online and accessible using APIs, several packages have been developed to
interact and download these datasets directly in R, thereby enabling direct and
reproducible analyses.  Notably, the organization rOpenSci
(\url{https://ropensci.org}) has fostered a community of researchers who develop
tools and methods to facilitate the use of open data as well broaden the
adoption of open science practices in general. For instance, the
rOpenSci-developed packge \texttt{TreeBase} \citep{Boettiger2012TB} allows users
to access phylogenies stored in treeBASE (\url{www.treebase.org}).
\texttt{rotl} contributes to this initiative, and greatly extends the number of
taxa for which phylogenetic data can be retrieved within R, while allowing the
data from OTL to be combined with other sources easily.

>>>>

In recent years, R has become an essential part of the toolbox of many
researchers in evolutionary biology. R greatly facilitates the analysis of large
datasets, and allows researchers to combine methods in novel ways because many
methods for comparative analyses are implemented, and because it is a relatively
easy to use programming language. Additionally, as more data are made available
online and accessible using APIs, several packages have been developed to
interact and download these datasets directly in R, thereby enabling direct and
reproducible analyses.  Notably, the organization rOpenSci
(\url{https://ropensci.org}) has fostered a community of researchers who develop
tools and methods to facilitate the use of open data as well broaden the
adoption of open science practices in general. For instance, the
rOpenSci-developed package \texttt{TreeBase} \citep{Boettiger2012TB} allows users
to access phylogenies stored in treeBASE (\url{www.treebase.org}).
\texttt{rotl} contributes to this initiative, and greatly extends the number of
taxa for which phylogenetic data can be retrieved within R, while allowing the
data from OTL to be combined with other sources easily.
